Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-04 intro.tex
clarify and add citation about rice's theorem

% paragraph to appease the theoretician in me
It is worth taking a moment to consider the theoretical possibility of
this task. We are not attempting to predict the state of the CPU at an
arbitrary point in the future --- this, at least with perfect
accuracy, would be tantamount to solving the halting problem. What we
are attempting is to predict aspects or functions of the running of
the CPU, e.g., processor efficiency and similar statistics. Prediction of these quantities
at some finite time in the future, even with perfect accuracy, does
not violate the Rice-Shapiro{\color{blue}[[Ryan: Do you have a citation for this theorem, also should we give a brief sentence explaining what this theorem is?]]} theorem.

>>>>

% paragraph to appease the theoretician in me
It is worth taking a moment to consider the theoretical possibility of
this task. We are not attempting to predict the state of the CPU at an
arbitrary point in the future --- this, at least with perfect
accuracy, would be tantamount to solving the halting problem. What we
are attempting is to predict aspects or functions of the running of
the CPU, e.g., processor efficiency and similar statistics. Prediction of these quantities
at some finite time in the future, even with perfect accuracy, does
not violate the Rice-Shapiro theorem~\cite{hopcroft} which essentially states that any non-trivial property of a program is uncomputable.
